Enforcing Boundaries: China's Overseas NGO Law and Operational Constraints for Global Civil Society

### 2024-01-19 manuscript/manuscript.qmd
revised the Introduction sections
- use clearer explanation of the research questions and how the constructs of de jure and de facto are embedded
- No longer using mixed method

In this paper, we use the case of China to explore how demands to both restrict and embrace INGOs have shaped the international nonprofit sector in the five years since the 2016 ONGO Law came into effect. We examine how the ONGO Law has influenced the population of INGOs that have successfully registered in China, as well as the association between factors such as INGO issue areas and the operational space granted to them in the country. We contribute to a growing body of research on the effects of closing civic space on INGO behavior and strategies. First, we expand work that uses institutional approaches to understanding civil society regulations, which argues that states strategically regulate INGOs to maintain regime stability, choosing forms of regulation and repression that minimize threats to internal political stability [@Chaudhry:2022; @DeMattee:2018; @DeMattee:2019; @Heiss:2019]. Second, we explore how authoritarian civil society regulations act as policy tools that regimes can leverage to shift INGO behavior in their favor and how these laws reshape and tame organizational strategies [@Li:2020; @LianMurdie:2023]. Third, we explore how these regulations lead to differentiated application of the law depending on organizational characteristics. We argue that INGO issue areas, missions, and pre-existing relationships with local government officials influence the degree of operating space available for INGOs.

By focusing on INGO operational space in China, we provide a unique empirical view into the *de facto* regulatory environment for foreign civil society in an authoritarian state. General indexes of civil society openness---such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022]---capture the regulatory environment for civil society more broadly, but do not reflect the specific implementation of laws for INGOs. In this paper, we use a mixed methods approach to explore the regulatory environment for INGOs in particular, providing a richer description and analysis of the impact of INGO laws.

Below, we provide a brief overview of China's 2016 ONGO Law and the different regulatory mechanisms it provides for INGOs to obtain legal access to the country. We then synthesize existing research on authoritarian regulation of INGOs and the differential application of these laws based on regime preferences and organizational characteristics, and propose a set of theoretical expectations based on this literature. We test these expectations with a mixed methods research design, combining Bayesian analysis of administrative data from all `r nrow(ongo)` formally registered INGOs with a comparative case study of Greenpeace and The Nature Conservancy, two environmental INGOs that took different approaches to operating in China after 2017. We conclude with a broader discussion of authoritarian civil society regulations and propose future approaches for exploring the practical operating environment for INGOs working in such regimes.

>>>>

In this paper, we empirically study the case of China's ONGO Law to explore whether and how *de facto* execution of discretion by the government varies by different types of INGOs while *de jure* regulations are the same. Specifically, we analyze how factors including issue areas are associated with the operational space of INGOs, in terms of both successful registration and the geographical scope approved to operate in, drawing from administrative data of the five years since the 2016 ONGO Law came into effect. We contribute to a growing body of research on the effects of closing civic space on INGO behavior and strategies. First, we expand work that uses institutional approaches to understanding civil society regulations, which argues that states strategically regulate INGOs to maintain regime stability, choosing forms of regulation and repression that minimize threats to internal political stability [@Chaudhry:2022; @DeMattee:2018; @DeMattee:2019; @Heiss:2019]. Second, we explore how authoritarian civil society regulations act as policy tools that regimes can leverage to shift INGO behavior in their favor and how these laws reshape and tame organizational strategies [@Li:2020; @LianMurdie:2023]. Third, we explore how these regulations lead to differentiated application of the law depending on organizational characteristics. We argue that INGO issue areas, missions, and pre-existing relationships with local government officials influence the degree of operating space available for INGOs.

By focusing on INGO operational space in China, we provide a unique empirical view into the *de facto* regulatory environment for foreign civil society in an authoritarian state. General indexes of civil society openness---such as the core civil society index from the Varieties of Democracy project [@LianMurdie:2023; @ChaudhryHeiss:2022]---capture the regulatory environment for civil society more broadly, but do not reflect the specific implementation of laws for INGOs. Existing literature on China's ONGO Law mostly discussed the *de jure* legislation around the time when the law was implemented (to add reference) or reports case studies of how selected INGOs navigated the new legal framework shortly after the law took effect (to add reference). This paper is the first large N study of all registered INGOs and expands the time frame to the five years enforcement of the ONGO Law, providing insights for both scholars and practitioners on how the operational space of INGOs varies by issue areas and factors such as local connections.

Below, we provide a brief overview of China's 2016 ONGO Law and the different regulatory mechanisms it provides for INGOs to obtain legal access to the country. We then synthesize existing research on authoritarian regulation of INGOs and the differential application of these laws based on regime preferences and organizational characteristics, and propose a set of theoretical expectations based on this literature. We test these expectations with descriptive statistics and multilevel Bayesian modeling of administrative data from all `r nrow(ongo)` formally registered INGOs. We interpret and discuss the quantitative results by drawing from practical cases of INGOs practical survial strategies under the ONGO Law era. We conclude with a broader discussion of authoritarian civil society regulations and propose future approaches for exploring the practical operating environment for INGOs working in such regimes.
